{How do we copy and paste?\\The semantic drift of quotations in blogspace}

### 2014-12-12 brains-protocol.tex
morning build

>>>>

Manual inspection of this dataset revealed that it contains a significant number of everyday language quotations (such as ``it was much better than i expected'', ``did that just happen'', as well as many simple expletive-based sentences). Their presence is may largely owe to random variations around a casual expression, while we are interested in transformations of news-related quotes linked to an original, identifiable utterance. We thus filter out all clusters lasting more than 80 days, or featuring quotes having less than 5 words \cam{not sure this is what you meant [but then the filter may be a bit asymmetric, oder?]} (or not written in English).  We eventually keep 19,621 clusters (out of 71,568; i.e. 27.4\%), 60,246 quotes (out of 310,457; i.e. 19.4\%) and $\sim$838k occurrences (out of 8.12m, i.e. 10.3\%). The significantly larger loss in occurrences indicates that, on average, the clusters we lose feature more occurrences than those we keep, which is expected for everyday language utterances.\footnote{While we lose real event-related utterances such as ``the terrorists have used automatic weapons and in some places grenades have been lobbed the encounters are still going on and we are trying to overpower them'', we contend that the use of the unfiltered dataset would strongly jeopardize results related to linguistic evolution or information diffusion. We could manually check on a subsample of clusters that a large proportion of remaining quotes seem to be relevant, while filtered quotes are essentially irrelevant.}
